%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {NSERC CREATE Trainee Intern} % Job title
    {University of Toronto -- Atmospheric Physics -- under Prof. K. Walker (no relation)} % Organization
    {Toronto, Canada} % Location
    {May. 2010 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Automated execution of spectral analysis for data collected by the
            PARIS-IR spectrometer.}
        \item{Traveled to Dalhousie University and set up the PARIS-IR
            spectrometer on site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PHY371Y1Y -- Supervised Study in Physics (Course) -- \emph{Quantum
        Information and Measurement}} % Job title
    {University of Toronto -- under Prof. A. Steinberg} % Organization
    {Toronto, Canada} % Location
    {Sep. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Studied quantum computing theory.}
      \item{Studied quantum information theory.}
      \item{Read research papers on the subjects of quantum discord,
          deterministic quantum computing with one qubit (DQC1), sharing
          entanglement without communicating non-separable states.}
      \item{Produced report and presentation to Prof. Steinberg and the Physics
          Dept. Undergraduate Chair on the topic of quantum discord.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CQIQC Summer Studentship Award Recipient} % Job title
    {University of Toronto -- Chemical Physics Theory Group -- under Prof. P. Brumer} % Organization
    {Toronto, Canada} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Learned the quantum Liouville formalism to investigate the Hilbert
            space structure of classical mechanics.}
        \item{Provided proofs for classical analogues of the no-cloning theorem
            and teleportation schemes in continuous variable systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CHM499Y1Y -- Introduction to Chemistry Research (Course)} % Job title
    {University of Toronto -- Chemical Physics Theory Group -- under Prof. P. Brumer} % Organization
    {Toronto, Canada} % Location
    {Sep. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed a novel theoretical test for entanglement of a
            wavefunction in continuous variable systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Paid Research Position} % Job title
    {University of Toronto -- Chemical Physics Theory Group -- under Prof. P. Brumer} % Organization
    {Toronto, Canada} % Location
    {May 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Extended above wavefunction test to study the dynamics of entanglement
            in continuous and discrete variable systems.}
        \item{Derived evolutionary equation for entanglement in general pure systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
